---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pg

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/pg)](https://CRAN.R-project.org/package=pg)
<!-- badges: end -->

The name of the package (Papa Golf) reflects the fundamental dependency: PostgreSQL. The functions support connection to PostgreSQL databases either using `RPostgres` or by `odbc`.

The goal of `pg` is to encapsulate PostgreSQL-specific queries using `dplyr`, `dbplyr` and `DBI` packages.

## Installation

You can install the development version of pg like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pg)
## basic example code
```
